Labeled object representation and manipulation with ITK

### 2007-08-31 article/Article.tex
perimeter and roundness attributes
darcs-hash:20070830153052-2fc9d-c530751e06bee8f0d8482e861c050092a03fc7ce.gz
add some doc
darcs-hash:20070831102836-2fc9d-c94e480bc3fbc4c3f4a327d7342b0d0c6f65c38f.gz

Once the manipulation of the objects is done, it can be useful to go back to a
more classic {\em itk::Image}. Several classes are provided to do that:
\begin{itemize}
  \item The {\em itk::LabelCollectionImageToLabelImageFilter} class simply
convert a {\em itk::LabelCollectionImage} to a labeled image stored in a {\em
itk::Image}.
  \item The {\em itk::LabelCollectionImageToBinaryImageFilter} put all the
objects in the foreground of a binary image stored in a {itk::Image}. It is
intended to be used with an image produced by the {\em
itk::BinaryImageToLabelCollectionImageFilter}. The background values of the
original image can also be restored by this filter.
  \item The {\em itk::LabelCollectionImageToMaskImageFilter} class can be used
to mask an image with the objects of the {\em itk::LabelCollectionImage}.
  \item Finally, {\em itk::LabelCollectionImageToAttributeImageFilter} produce
an {\em itk::Image} with the value of the attribute of the objects of the {\em
itk::LabelCollectionImage}. This filter is mostly useful to have a global view
of the attribute values in the image.
\end{itemize}

@@

\begin{eqnarray}
R = {\frac{a}{A_n(r)}}
\end{eqnarray}

@@

@@

>>>>

Once the manipulation of the objects is done, it can be useful to go back to a
more classic {\em itk::Image}. Several classes are provided to do that:
\begin{itemize}
  \item The {\em itk::LabelCollectionImageToLabelImageFilter} class simply
convert a {\em itk::LabelCollectionImage} to a labeled image stored in a {\em
itk::Image}.
  \item The {\em itk::LabelCollectionImageToBinaryImageFilter} put all the
objects in the foreground of a binary image stored in a {itk::Image}. It is
intended to be used with an image produced by the {\em
itk::BinaryImageToLabelCollectionImageFilter}. The background values of the
original image can also be restored by this filter.
  \item The {\em itk::LabelCollectionImageToMaskImageFilter} class can be used
to mask an image with the objects of the {\em itk::LabelCollectionImage}. With
that filter, the image can be cropped to contain only the masked zone, or the
masked zone padded by a user defined number of pixels.
  \item Finally, {\em itk::LabelCollectionImageToAttributeImageFilter} produce
an {\em itk::Image} with the value of the attribute of the objects of the {\em
itk::LabelCollectionImage}. This filter is mostly useful to have a global view
of the attribute values in the image.
\end{itemize}

@@

\begin{eqnarray}
R = {\frac{A_n(r)}{a}}
\end{eqnarray}

@@

\subsection{Pixel's neighborhood}

The run-length encoding does not allow an easy access to the neighbors of a
given pixel. If the neighborhood of all the pixels must be accessed, it is
much easier to convert the {itk::LabelCollectionImage} to a {\em itk::Image}
with the {\em itk::LabelCollectionImageToLabelImageFilter}, and use that
image to access the neighbors. That's what is done in {\em itk::ShapeLabelCollectionImageFilter}
to compute the maximum Feret diameter, and the perimeter estimation.

@@

\subsection{The mask features}

The {\em itk::LabelCollectionImageToMaskImageFilter} class let the user mask
a part of an {\em itk::Image} with the objects of a {\em itk::LabelCollectionImage}.
It can also crop the image to contain only the masked region.

The source code is available in the file {\em mask.cxx}.

#include "itkLabelObject.h"
#include "itkLabelCollectionImage.h"
#include "itkLabelImageToLabelCollectionImageFilter.h"
#include "itkLabelCollectionImageToMaskImageFilter.h"

  if( argc != 9 )
    {
    std::cerr << "usage: " << argv[0] << " labelImage input output label bg neg crop cropBorder" << std::endl;
    // std::cerr << "  : " << std::endl;
    exit(1);
    }
\end{verbatim} \normalsize
the filters are able to work in any dimension. Lets choose 3, so the program can be tested on
2D and 2D image.
\small \begin{verbatim}
  const int dim = 3;
\end{verbatim} \normalsize
declare the input image type
\small \begin{verbatim}
  typedef itk::Image< unsigned char, dim > ImageType;
\end{verbatim} \normalsize
and the label object type to use. The input image is a label image, so the 
type of the label can be the same type than the pixel type. itk::LabelObject is
chosen, because only the mask feature is tested here, so we don't need any
attribute.
\small \begin{verbatim}
  typedef itk::LabelObject< unsigned char, dim > LabelObjectType;
  typedef itk::LabelCollectionImage< LabelObjectType > LabelCollectionImageType;
\end{verbatim} \normalsize
read the label image and the input image to be masked.
\small \begin{verbatim}
  typedef itk::ImageFileReader< ImageType > ReaderType;
  ReaderType::Pointer reader = ReaderType::New();
  reader->SetFileName( argv[1] );

  ReaderType::Pointer reader2 = ReaderType::New();
  reader2->SetFileName( argv[2] );
\end{verbatim} \normalsize
convert the label image to a label collection image.
\small \begin{verbatim}
  typedef itk::LabelImageToLabelCollectionImageFilter< ImageType, LabelCollectionImageType> I2LType;
  I2LType::Pointer i2l = I2LType::New();
  i2l->SetInput( reader->GetOutput() );
  i2l->SetUseBackground( true );
\end{verbatim} \normalsize
then mask the image. Two inputs are required (the label collection image, and
the image to be masked). The label used to mask the image is passed with the 
{\em SetLabel()} method. The background in the output image, where the image is masked,
is passed with {\em SetBackground()}. The user can choose to mask the image outside the
label object (that's the default behavior), or inside the label object with the
chosen label, by calling {\em SetNegated()}. Finally, the image can be cropped to the
masked region, by calling {\em SetCrop(true)}, or to a region padded by a border, by
calling both {\em SetCrop()} and {\em SetCropBorder()}. The crop border defaults to $0$, and the
image is not cropped by default.
\small \begin{verbatim}
  typedef itk::LabelCollectionImageToMaskImageFilter< LabelCollectionImageType, ImageType > MaskType;
  MaskType::Pointer mask = MaskType::New();
  mask->SetInput( i2l->GetOutput() );
  mask->SetFeatureImage( reader2->GetOutput() );
  mask->SetLabel( atoi(argv[4]) );
  mask->SetBackgroundValue( atoi(argv[5]) );
  mask->SetNegated( atoi(argv[6]) );
  mask->SetCrop( atoi(argv[7]) );
  MaskType::SizeType border;
  border.Fill( atoi(argv[8]) );
  mask->SetCropBorder( border );
  itk::SimpleFilterWatcher watcher6(mask, "filter");
\end{verbatim} \normalsize
Finally, save the output image.
\small \begin{verbatim}
  typedef itk::ImageFileWriter< ImageType > WriterType;
  WriterType::Pointer writer = WriterType::New();
  writer->SetInput( mask->GetOutput() );
  writer->SetFileName( argv[3] );
  writer->Update();
